karate

### 2021-02-23 inst/karate.Rmd
rewording

Here I analyse a [karate](https://en.wikipedia.org/wiki/Karate)
dataset taken from
[https://en.wikipedia.org/wiki/2018_World_Karate_Championships].

>>>>

Here I analyse a [karate](https://en.wikipedia.org/wiki/Karate)
dataset taken from
[wikipedia](https://en.wikipedia.org/wiki/2018_World_Karate_Championships).
